R Notebook

### 2018-10-15 main_bookcliff.Rmd
cleaning

okay, if we want to fit these transiograms, we need to implement non stationarity
therefore, we need to compute the proportion on each horizontal 
```{r}
prop1=prop2=prop3=numeric(nrow(env_lat))
for (i in 1:nrow(env_lat)){
  prop1[i]=mean(i1[i,],na.rm=TRUE)
  prop2[i]=mean(i2[i,],na.rm=TRUE)
  prop3[i]=mean(i3[i,],na.rm=TRUE)
}
plot(1:nrow(i1),prop1,type = "l")
plot(1:nrow(i1),prop2,type = "l")
plot(1:nrow(i1),prop3,type = "l")
```
ok we are trying to smooth the curves with moving average
```{r}
f50=rep(1/50,50)
prop1filter<-filter(prop1,f50,sides=2)
prop1filter[542:566]=prop1[542:566]
prop1filter[1:24]=prop1[1:24]
plot(1:nrow(i1),prop1filter,type = "l")
#prop2filter<-filter(prop2,f50,sides=2)
#prop2filter[542:566]=prop2[542:566]
#prop2filter[1:24]=prop2[1:24]
#plot(1:nrow(i1),prop2filter,type = "l")
prop3filter<-filter(prop3,f50,sides=2)
prop3filter[542:566]=prop3[542:566]
prop3filter[1:24]=prop3[1:24]
plot(1:nrow(i1),prop3filter,type = "l")
prop2filter=1-prop1filter-prop3filter
plot(1:nrow(i1),prop2filter,type = "l")
#prop1filter+prop2filter+prop3filter
```
we want to plot an image with those curves
```{r}
png(file="PCvert.png",width=2000,height = 800,res=300,antialias = )
par(mar=c(0,0,0,0))
n=nrow(i1)
plot(1:n,prop2filter+prop3filter,type="l",axes=FALSE,ann=FALSE)
lines(1:n,prop3filter)
lines(1:n,rep(1,n))
lines(1:n,rep(0,n))
```

ok now we need to compute the theoretical transiograms with the accurate proportions
this is not good because the global proportions also depend on the horizontal PC
```{r}
rv1=5
rv2=5
b1=0
b2=0
rho=0
n=nrow(i1)
# ok so the thresolds depends on the z, we have a vector
q1=q2=numeric(n)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
for (z in 1:n){
  q1[z]=qnorm(prop1filter[z])
  obj=Inf
  for(test in 1:100){
    q2test = qnorm(test/100)
    newobj =abs( pmvnorm(lower=c(q1[z],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - prop2filter[z] ) 
    if (newobj < obj){
    q2[z] = q2test
    obj = newobj
    }
  }
}
```
```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
```

transiograms now only with vertical proportion curves
```{r}
x = (1:200)/10.
t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,200)
Sigma = diag(1,4)
for (i in 1:200){
    t1=t2=t3=0
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
    for (z in 1:(n-i)){
      if (prop1filter[z]!=0){
        t11_model[i]=t11_model[i]+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z],Inf,q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]
        t12_model[i]=t12_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i],q2[z+i]),upper=c(q1[z],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]  
        t13_model[i]=t13_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i],-Inf),upper=c(q1[z],Inf,Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]
        t1= t1+1
      }

      if(prop2filter[z]!=0){
        t21_model[i]=t21_model[i]+pmvnorm(lower=c(q1[z],q2[z],-Inf,-Inf),upper=c(Inf,Inf,q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
        t22_model[i]=t22_model[i]+pmvnorm(lower=c(q1[z],q2[z],q1[z+i],q2[z+i]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
        t23_model[i]=t23_model[i]+pmvnorm(lower=c(q1[z],q2[z],q1[z+i],-Inf),upper=c(Inf,Inf,Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
        t2=t2+1
      }

      if(prop3filter[z]!=0){
        t31_model[i]=t31_model[i]+pmvnorm(lower=c(q1[z],-Inf,-Inf,-Inf),upper=c(Inf,q2[z],q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
        t32_model[i]=t32_model[i]+pmvnorm(lower=c(q1[z],-Inf,q1[z+i],q2[z+i]),upper=c(Inf,q2[z],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
        t33_model[i]=t33_model[i]+pmvnorm(lower=c(q1[z],-Inf,q1[z+i],-Inf),upper=c(Inf,q2[z],Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
        t3=t3+1
      }

    }
    t11_model[i]=t11_model[i]/t1
    t12_model[i]=t12_model[i]/t1
    t13_model[i]=t13_model[i]/t1
    t21_model[i]=t21_model[i]/t2
    t22_model[i]=t22_model[i]/t2
    t23_model[i]=t23_model[i]/t2
    t31_model[i]=t31_model[i]/t3
    t32_model[i]=t32_model[i]/t3
    t33_model[i]=t33_model[i]/t3

}

par(mfrow=c(3,3))
plot(x,t11exp,type="l",ylim=c(0,1))
lines(x,t11_model,lwd=2)
plot(x,t12exp,type="l",ylim=c(0,1))
lines(x,t12_model,lwd=2)
plot(x,t13exp,type="l",ylim=c(0,1))
lines(x,t13_model,lwd=2)
plot(x,t21exp,type="l",ylim=c(0,1))
lines(x,t21_model,lwd=2)
plot(x,t22exp,type="l",ylim=c(0,1))
lines(x,t22_model,lwd=2)
plot(x,t23exp,type="l",ylim=c(0,1))
lines(x,t23_model,lwd=2)
plot(x,t31exp,type="l",ylim=c(0,1))
lines(x,t31_model,lwd=2)
plot(x,t32exp,type="l",ylim=c(0,1))
lines(x,t32_model,lwd=2)
plot(x,t33exp,type="l",ylim=c(0,1))
lines(x,t33_model,lwd=2)
```

The transiograms are still not perfect, we need to also put a lateral non stationarity

okay, if we want to fit these transiograms, we need to implement non stationarity
therefore, we need to compute the proportion on each horizontal 
```{r}
prop1lat=prop2lat=prop3lat=numeric(ncol(env_lat))
for (i in 1:ncol(env_lat)){
  prop1lat[i]=mean(i1[,i],na.rm=TRUE)
  prop2lat[i]=mean(i2[,i],na.rm=TRUE)
  prop3lat[i]=mean(i3[,i],na.rm=TRUE)
}
plot(1:ncol(i1),prop1lat,type = "p")
plot(1:ncol(i1),prop2lat,type = "p")
plot(1:ncol(i1),prop3lat,type = "p")
```
now doing a good figure
```{r}
png(file="PChor.png",width=2000,height = 800,res=300,antialias = )
par(mar=c(0,0,0,0))
n=ncol(i1)
plot(1:n,prop2lat+prop3lat,type="p",axes=FALSE,ann=FALSE,ylim=c(0,1))
lines(1:n,prop3lat,type="p")
lines(1:n,rep(1,n))
lines(1:n,rep(0,n))
```

we are now doing the mean of the lateral and vertical proportion curves
```{r}
prop1mat=prop2mat=prop3mat=matrix(0,nrow=nrow(env_lat),ncol=ncol(env_lat))
for ( i in 1:nrow(env_lat)){
  for (j in 1:ncol(env_lat)){
    prop1mat[i,j]=(prop1filter[i]+prop1lat[j])/2
    prop2mat[i,j]=(prop2filter[i]+prop2lat[j])/2
    #prop3mat[i,j]=(prop3filter[i]+prop3lat[j])/2
  }
}
prop3mat=1-prop2mat-prop1mat
prop3mat[prop3mat<0]=0
image(prop1mat)
image(prop2mat)
image(prop3mat)
```
thresholds this one need to be the same that on the whole grid

```{r}
#this one is not precise enough
n=nrow(i1)
m=ncol(i1)
q1=q2=matrix(0,n,m)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
for (z in 1:n){
  for(x in 1:m){
    q1[z,x]=qnorm(prop1mat[z,x])
    obj=Inf
    for(test in 1:10){
      q2test = qnorm(test/10)
      newobj =abs( pmvnorm(lower=c(q1[z,x],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - prop2mat[z,x] ) 
      if (newobj < obj){
      q2[z,x] = q2test
      obj = newobj
      }
    }
  }
}
```
we implement an analytic way to compute the thresholds
```{r}
n=nrow(i1)
m=ncol(i1)
q1=q2=matrix(0,n,m)
for (z in 1:n){
  for(x in 1:m){
      q1[z,x]=qnorm(prop1mat[z,x])
      if (prop3mat[z,x]!=0) {
      q2[z,x]=qnorm(1-(prop2mat[z,x]/(1-prop1mat[z,x])))
      }
      else{q2[z,x]=-Inf}
  }
}
```

the transios now with vertical and horizontal proportion curves
```{r}
rv1=0.5
rv2=0.5
b1=0
b2=0
rho=0
n=nrow(i1)
m=ncol(i1)
d = (1:200)/10.
t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,200)
Sigma = diag(1,4)
for (i in 1:200){
    t1=t2=t3=0
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
    for (z in 1:(n-i)){
      for ( x in 1:m){
        if (prop1mat[z,x]!=0){
          t11_model[i]=t11_model[i]+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z,x],Inf,q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t12_model[i]=t12_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i,x],q2[z+i,x]),upper=c(q1[z,x],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]  
          t13_model[i]=t13_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i,x],-Inf),upper=c(q1[z,x],Inf,Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t1= t1+1
        }

        if(prop2mat[z,x]!=0){
          t21_model[i]=t21_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],-Inf,-Inf),upper=c(Inf,Inf,q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t22_model[i]=t22_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+i,x],q2[z+i,x]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t23_model[i]=t23_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+i,x],-Inf),upper=c(Inf,Inf,Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t2=t2+1
        }

        if(prop3mat[z,x]!=0){
          t31_model[i]=t31_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,-Inf,-Inf),upper=c(Inf,q2[z,x],q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t32_model[i]=t32_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+i,x],q2[z+i,x]),upper=c(Inf,q2[z,x],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t33_model[i]=t33_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+i,x],-Inf),upper=c(Inf,q2[z,x],Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t3=t3+1
        }
      }

    }
    t11_model[i]=t11_model[i]/t1
    t12_model[i]=t12_model[i]/t1
    t13_model[i]=t13_model[i]/t1
    t21_model[i]=t21_model[i]/t2
    t22_model[i]=t22_model[i]/t2
    t23_model[i]=t23_model[i]/t2
    t31_model[i]=t31_model[i]/t3
    t32_model[i]=t32_model[i]/t3
    t33_model[i]=t33_model[i]/t3

}
d = (1:200)/10.
par(mfrow=c(3,3))
plot(d,t11exp,type="l",ylim=c(0,1))
lines(d,t11_model,lwd=2)
plot(d,t12exp,type="l",ylim=c(0,1))
lines(d,t12_model,lwd=2)
plot(d,t13exp,type="l",ylim=c(0,1))
lines(d,t13_model,lwd=2)
plot(d,t21exp,type="l",ylim=c(0,1))
lines(d,t21_model,lwd=2)
plot(d,t22exp,type="l",ylim=c(0,1))
lines(d,t22_model,lwd=2)
plot(d,t23exp,type="l",ylim=c(0,1))
lines(d,t23_model,lwd=2)
plot(d,t31exp,type="l",ylim=c(0,1))
lines(d,t31_model,lwd=2)
plot(d,t32exp,type="l",ylim=c(0,1))
lines(d,t32_model,lwd=2)
plot(d,t33exp,type="l",ylim=c(0,1))
lines(d,t33_model,lwd=2)
```
After discussion, it is more interesting to only look at the transition rates between facies.
In that case, it is not necessary to take into account the non stationary proportions

```{r}
q1g=qnorm(p1)
q2g=qnorm(1-(p2/(1-p1)))
```

```{r}
rv1=0.6
rv2=0.7
Sigma = diag(1,4)
d = 1/10
Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
r11_model=(1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1g,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p1)
r12_model=pmvnorm(lower=c(-Inf,-Inf,q1g,q2g),upper=c(q1g,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/(p1)
r13_model=pmvnorm(lower=c(-Inf,-Inf,q1g,-Inf),upper=c(q1g,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p1
r21_model=pmvnorm(lower=c(q1g,q2g,-Inf,-Inf),upper=c(Inf,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2
r22_model=(1-pmvnorm(lower=c(q1g,q2g,q1g,q2g),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2)
r23_model=pmvnorm(lower=c(q1g,q2g,q1g,-Inf),upper=c(Inf,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p2
r31_model=pmvnorm(lower=c(q1g,-Inf,-Inf,-Inf),upper=c(Inf,q2g,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
r32_model=pmvnorm(lower=c(q1g,-Inf,q1g,q2g),upper=c(Inf,q2g,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
r33_model=(1-pmvnorm(lower=c(q1g,-Inf,q1g,-Inf),upper=c(Inf,q2g,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p3)
matrix(c(0,r12_model/r11_model,r13_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r31_model/r33_model,r32_model/r33_model,0),3,3,byrow=TRUE)

@@

I finally think that we cannot suppose stationnarity even for the transition rates. 
Therefore I will compute them in the case of non stationarity
```{r}
rv1=5
rv2=5
b1=0
b2=0
rho=0
n=nrow(i1)
m=ncol(i1)

t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=0
Sigma = diag(1,4)
  t1=t2=t3=0
    d = 1/10.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
    for (z in 1:(n-1)){
      for ( x in 1:m){
        if (prop1mat[z,x]!=0){
          t11_model=t11_model+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z,x],Inf,q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t12_model=t12_model+pmvnorm(lower=c(-Inf,-Inf,q1[z+1,x],q2[z+1,x]),upper=c(q1[z,x],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]  
          t13_model=t13_model+pmvnorm(lower=c(-Inf,-Inf,q1[z+1,x],-Inf),upper=c(q1[z,x],Inf,Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t1= t1+1
        }

        if(prop2mat[z,x]!=0){
          t21_model=t21_model+pmvnorm(lower=c(q1[z,x],q2[z,x],-Inf,-Inf),upper=c(Inf,Inf,q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t22_model=t22_model+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+1,x],q2[z+1,x]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t23_model=t23_model+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+1,x],-Inf),upper=c(Inf,Inf,Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t2=t2+1
        }

        if(prop3mat[z,x]!=0){
          t31_model=t31_model+pmvnorm(lower=c(q1[z,x],-Inf,-Inf,-Inf),upper=c(Inf,q2[z,x],q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t32_model=t32_model+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+1,x],q2[z+1,x]),upper=c(Inf,q2[z,x],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t33_model=t33_model+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+1,x],-Inf),upper=c(Inf,q2[z,x],Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t3=t3+1
        }
      }

    }
    t11_model=(1-t11_model/t1)*100
    t12_model=(t12_model/t1)*100
    t13_model=(t13_model/t1)*100
    t21_model=(t21_model/t2)*100
    t22_model=(1-t22_model/t2)*100
    t23_model=(t23_model/t2)*100
    t31_model=(t31_model/t3)*100
    t32_model=(t32_model/t3)*100
    t33_model=(1-t33_model/t3)*100

matrix(c(0,t12_model/t11_model,t13_model/t11_model,t21_model/t22_model,0,t23_model/t22_model,t31_model/t33_model,t32_model/t33_model,0),3,3,byrow=TRUE)    
```

okay now we create a grid (3d) to simulate the facies 
we will see if the transiograms really matter

@@

we are printing in a file 
```{r}
im<-array(NA,c(100,1,566))
im[5,1,]<-env_lat[,1]
im[6,1,]<-env_lat[,1]
im[15,1,]<-env_lat[,2]
im[16,1,]<-env_lat[,2]
im[25,1,]<-env_lat[,3]
im[26,1,]<-env_lat[,3]
im[35,1,]<-env_lat[,4]
im[36,1,]<-env_lat[,4]
im[45,1,]<-env_lat[,5]
im[46,1,]<-env_lat[,5]
im[55,1,]<-env_lat[,6]
im[56,1,]<-env_lat[,6]
im[65,1,]<-env_lat[,7]
im[66,1,]<-env_lat[,7]
im[75,1,]<-env_lat[,8]
im[76,1,]<-env_lat[,8]
im[85,1,]<-env_lat[,9]
im[86,1,]<-env_lat[,9]
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
png(file="logsutah.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```

@@

```{r}
gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)
#now we need to retrend the results
gridprop1krig=gridprop1krig+p1
gridprop2krig=gridprop2krig+p2
err=1-gridprop1krig-gridprop2krig
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      if (err[x,y,z]<0){
        gridprop1krig[x,y,z]=gridprop1krig[x,y,z]+err[x,y,z]
      }
    }
  }
}

image(gridprop1krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
image(gridprop2krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
gridprop3krig<-1-gridprop2krig-gridprop1krig
image(gridprop3krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1 , 200,300)], xpd = NA)
```
```{r}
gridprop1krig[gridprop1krig>1]
gridprop2krig[gridprop2krig>1]
gridprop1krig[gridprop1krig<0]
gridprop2krig[gridprop2krig<0]
```

@@

```{r}
source("functions.R")
```

>>>>

if we want to fit these transiograms, we need to implement non stationarity
therefore, we need to compute the proportion on each horizontal 
```{r}
prop1=prop2=prop3=numeric(nrow(env_lat))
for (i in 1:nrow(env_lat)){
  prop1[i]=mean(i1[i,],na.rm=TRUE)
  prop2[i]=mean(i2[i,],na.rm=TRUE)
  prop3[i]=mean(i3[i,],na.rm=TRUE)
}
plot(1:nrow(i1),prop1,type = "l")
plot(1:nrow(i1),prop2,type = "l")
plot(1:nrow(i1),prop3,type = "l")
```
ok we are now smoothing the curves with moving average
```{r}
f50=rep(1/50,50)
prop1filter<-filter(prop1,f50,sides=2)
prop1filter[542:566]=prop1[542:566]
prop1filter[1:24]=prop1[1:24]
plot(1:nrow(i1),prop1filter,type = "l")

prop3filter<-filter(prop3,f50,sides=2)
prop3filter[542:566]=prop3[542:566]
prop3filter[1:24]=prop3[1:24]
plot(1:nrow(i1),prop3filter,type = "l")
prop2filter=1-prop1filter-prop3filter
plot(1:nrow(i1),prop2filter,type = "l")

```
we want to plot an image with those curves
```{r}
png(file="PCvert.png",width=2000,height = 800,res=300,antialias = )
par(mar=c(0,0,0,0))
n=nrow(i1)
plot(1:n,prop2filter+prop3filter,type="l",axes=FALSE,ann=FALSE)
lines(1:n,prop3filter)
lines(1:n,rep(1,n))
lines(1:n,rep(0,n))
```

ok now we need to compute the theoretical transiograms with the accurate proportions
this is not good because the global proportions also depend on the horizontal PC

```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
```

okay, if we want to fit these transiograms, we need to implement non stationarity
therefore, we need to compute the proportion on each vertical 
```{r}
prop1lat=prop2lat=prop3lat=numeric(ncol(env_lat))
for (i in 1:ncol(env_lat)){
  prop1lat[i]=mean(i1[,i],na.rm=TRUE)
  prop2lat[i]=mean(i2[,i],na.rm=TRUE)
  prop3lat[i]=mean(i3[,i],na.rm=TRUE)
}
plot(1:ncol(i1),prop1lat,type = "p")
plot(1:ncol(i1),prop2lat,type = "p")
plot(1:ncol(i1),prop3lat,type = "p")
```
now doing a good figure
```{r}
png(file="PChor.png",width=2000,height = 800,res=300,antialias = )
par(mar=c(0,0,0,0))
n=ncol(i1)
plot(1:n,prop2lat+prop3lat,type="p",axes=FALSE,ann=FALSE,ylim=c(0,1))
lines(1:n,prop3lat,type="p")
lines(1:n,rep(1,n))
lines(1:n,rep(0,n))
```

we are now doing the mean of the lateral and vertical proportion curves
```{r}
prop1mat=prop2mat=prop3mat=matrix(0,nrow=nrow(env_lat),ncol=ncol(env_lat))
for ( i in 1:nrow(env_lat)){
  for (j in 1:ncol(env_lat)){
    prop1mat[i,j]=(prop1filter[i]+prop1lat[j])/2
    prop2mat[i,j]=(prop2filter[i]+prop2lat[j])/2
    #prop3mat[i,j]=(prop3filter[i]+prop3lat[j])/2
  }
}
prop3mat=1-prop2mat-prop1mat
prop3mat[prop3mat<0]=0
image(prop1mat)
image(prop2mat)
image(prop3mat)
```
Now that we have the proportions on the grid
we can compute the corresponding thresholds of the Gaussian functions according to the truncation rule

We can compute the thresholds analytically if the Gaussian functions are not correlated to each other here
```{r}
n=nrow(i1)
m=ncol(i1)
q1=q2=matrix(0,n,m)
for (z in 1:n){
  for(x in 1:m){
      q1[z,x]=qnorm(prop1mat[z,x])
      if (prop3mat[z,x]!=0) {
      q2[z,x]=qnorm(1-(prop2mat[z,x]/(1-prop1mat[z,x])))
      }
      else{q2[z,x]=-Inf}
  }
}
```
Because of the non stationarity, it is more relevant to computed the transition rates between facies rather than the
transiograms
we can thus fit the method with the transition rates

thresholds according to the truncation rule
```{r}
q1g=qnorm(p1)
q2g=qnorm(1-(p2/(1-p1)))
```

```{r}
rv1=5
rv2=5
rh=800
b1=0
b2=0
rho=0
rv1=0.6
rv2=0.7
Sigma = diag(1,4)
d = 1/10
Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
r11_model=(1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1g,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p1)
r12_model=pmvnorm(lower=c(-Inf,-Inf,q1g,q2g),upper=c(q1g,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/(p1)
r13_model=pmvnorm(lower=c(-Inf,-Inf,q1g,-Inf),upper=c(q1g,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p1
r21_model=pmvnorm(lower=c(q1g,q2g,-Inf,-Inf),upper=c(Inf,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2
r22_model=(1-pmvnorm(lower=c(q1g,q2g,q1g,q2g),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2)
r23_model=pmvnorm(lower=c(q1g,q2g,q1g,-Inf),upper=c(Inf,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p2
r31_model=pmvnorm(lower=c(q1g,-Inf,-Inf,-Inf),upper=c(Inf,q2g,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
r32_model=pmvnorm(lower=c(q1g,-Inf,q1g,q2g),upper=c(Inf,q2g,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
r33_model=(1-pmvnorm(lower=c(q1g,-Inf,q1g,-Inf),upper=c(Inf,q2g,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p3)
matrix(c(0,r12_model/r11_model,r13_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r31_model/r33_model,r32_model/r33_model,0),3,3,byrow=TRUE)

@@

okay now we create a grid (3d) to simulate the facies

@@

we are printing this picture in a file 
```{r}
im<-array(NA,c(100,1,566))
im[5,1,]<-env_lat[,1]
im[6,1,]<-env_lat[,1]
im[15,1,]<-env_lat[,2]
im[16,1,]<-env_lat[,2]
im[25,1,]<-env_lat[,3]
im[26,1,]<-env_lat[,3]
im[35,1,]<-env_lat[,4]
im[36,1,]<-env_lat[,4]
im[45,1,]<-env_lat[,5]
im[46,1,]<-env_lat[,5]
im[55,1,]<-env_lat[,6]
im[56,1,]<-env_lat[,6]
im[65,1,]<-env_lat[,7]
im[66,1,]<-env_lat[,7]
im[75,1,]<-env_lat[,8]
im[76,1,]<-env_lat[,8]
im[85,1,]<-env_lat[,9]
im[86,1,]<-env_lat[,9]
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
png(file="logsutah.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```

@@

```{r}
n=dim(gridprop1)
gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)
#now we need to retrend the results
gridprop1krig=gridprop1krig+p1
gridprop2krig=gridprop2krig+p2
err=1-gridprop1krig-gridprop2krig
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      if (err[x,y,z]<0){
        gridprop1krig[x,y,z]=gridprop1krig[x,y,z]+err[x,y,z]
      }
    }
  }
}

image(gridprop1krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
image(gridprop2krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
gridprop3krig<-1-gridprop2krig-gridprop1krig
image(gridprop3krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1 , 200,300)], xpd = NA)
```
test
```{r}
gridprop1krig[gridprop1krig>1]
gridprop2krig[gridprop2krig>1]
gridprop1krig[gridprop1krig<0]
gridprop2krig[gridprop2krig<0]
```

@@
